\startcomponent acknowledgement
\product dissertation

\page[yes]

\midaligned{\tfc\sc Acknowledgements}\blank[2*line]
\setupdelimitedtext[blockquote][style=\sl,before={\setupinterlinespace[line=2.4ex]}]
\startblockquote
I would like to express my sincere gratitude for those who have helped me during the course of preparation and along the way to conduct my research up until completion of my master thesis. \par
\blank[line]
First and foremost, I would like to thank my supervisor Dr Haider al-Khateeb for all his efforts, valuable feedback and guidance throughout the whole project. \par
His critical review of my work and experience in the field helped me achieving to find the right topic and keeping it to the standards I was aiming for. \par
During the work of my project I was able to improve and broaden my understanding of cyber-physical systems and gain knowledge on the cyber security topic in much greater detail. \par
\blank[line]
Furthermore, I am extremely lucky to have been taught by Gregory Epiphaniou during the entirety of the course and I would like to thank him for his advice and encouraging words and the time he has made available for discussing ideas around my topic and the vast amount of suggestions he made for relevant research papers. \par
\blank[line]
To my fellow students at the February 2015 cohort my greatest appreciation, particularly to Rafael Narezzi and Stefan Fernandes with whom I have bounced ideas and thoughts throughout the entirety of the course. Especially for all the discussions we have had around cyber security which has helped me shaping my dissertation to embrace contemporary views. \par
\blank[line]
Lastly, I am humbled to have been given the opportunity to study and to be enrolled on this masters course in cyber security, which was made possible through QA by Northumbria University. \par
\blank[line]
My thesis would not be complete without the help of my family and friends for proofreading as well as editing and therefore, I would like to give my gratitude to my sister Ágnes Reviczky-Balogh and my friend Clare Canton who taught me at the English Language Centre at King's College London. \par % Ekaterina Gerasimova
\stopblockquote

\stopcomponent
